##Installing required packages
```{r}
source("https://bioconductor.org/biocLite.R")
biocLite()
biocLite(c("affy", "limma")) ##Packages required for microarray analysis
```

##Loading packages
```{r}
library(magrittr)
library(affy)
library(limma)
library(gplots)
```

##Reading the microarray data from the file/folder
```{r}
##If you use Affymetrix chips your microarray data will consist of a series of CEL files containing raw intensities for each probe on the array. Save all CEL files you want to analyze in a single directory. They may be gzipped (*.gz) - you do not need to gunzip them
celfilepath = "/media/lab-admin/VS_lab_disk/Lakshmi_working_data/microarray_data_varadha/430B"

##Import all the CEL files by a single command using the ReadAffy() method. ReadAffy will read all CEL files in the folder and load them into an AffyBatch object in R
#Reading cel files
data <- ReadAffy(celfile.path = celfilepath)

target <- readTargets("list_cel_430B.txt", path = "/media/lab-admin/VS_lab_disk/Lakshmi_working_data/microarray_data_varadha/")

```

##Robust multi-array average (RMA) and extract the expression data and saving the expression data to a file
```{r}
# converts an AffyBatch object into an ExpressionSet object 
data_rma = rma(data, normalize = TRUE)

#Prepare expression matrix
exp <- data_rma@assayData$exprs

#Transfering the expression data to the desired folder
write.table(data_rma, "/media/lab-admin/VS_lab_disk/Lakshmi_working_data/microarray_data_varadha/output_430B/normalised_RMA.eset")

exp %>% as.data.frame() %>% write.csv("/media/lab-admin/VS_lab_disk/Lakshmi_working_data/microarray_data_varadha/output_430B/expression_data.csv")

```

## To access the genes differentially expressed between late infection and early infection

### first the variability of the data was assessed by fitting a linear model which modelled the systematic part of the data.

```{r, eval=TRUE, echo=TRUE}
d <- model.matrix(~ 0 + factor(target$file))
colnames(d) <- levels(factor(target$file))
fit.rma <- lmFit(data_rma, d)
hmcols <- colorRampPalette(c("red", "white", "blue"))(n=256) ##color palette for Heatmap
```

```{r, eval=TRUE, echo=TRUE}
#cont.mat <- makeContrasts(A1A_10_11_clo1 = "A1A_10_11_clone1-A1A_21_emptyvector",
 #                         A1A_3_10_clo2 = "A1A_3_10_clone2-A1A_21_emptyvector",
  #                        A2A_10_11_clo1 = "A2A_10_11_clone1-A2A_21_emptyvector",
   #                       A2A_3_10_clo2 = "A2A_3_10_clone2-A2A_21_emptyvector",
    #                      levels=d)

cont.mat <- makeContrasts(B_10_11_clo1 = "B_10_11_clone1-B_21_emptyvector",
                          B_3_10_clo2 = "B_3_10_clone2-B_21_emptyvector",
                          levels=d)

fit.1.rma <- contrasts.fit(fit.rma,
                           cont.mat)
```


### Then the differential expression was calculated by empirical Bayes shrinkage which moderated the standard deviations between genes.

```{r, eval=TRUE, echo=TRUE}
fit.1.rma <- eBayes(fit.1.rma)
```

### To assess significance and differential expression (DE), so that the expected false discovery rate is less than 5%.
```{r, eval=TRUE, echo=TRUE}
#Methods are the corrections made to the p-value. Basically a factor is multiplied to P-values. There are different methods in which this can be done. "fdr" seems to robust method to control the false discovery rate. 
selection_pvalue <- p.adjust(fit.1.rma$p.value[,2], method = "fdr") < 0.05   

dat_sel <- fit.1.rma[selection_pvalue, ]

results <- decideTests(fit.1.rma, method = "separate", adjust.method = "fdr", p.value = 0.05, lfc = 1) #lfc is log fold change should be 1

```

### Extract a table of the top-ranked genes from a linear model fit
```{r, eval=TRUE, echo=TRUE}
results_top <- topTable(fit.1.rma, coef = 2, adjust.method = "fdr", p.value = 0.05, lfc = 1, number = 10000)  #topTable give the list of differentially expressed genes. "number" is that to give that many number of entries from the toptable list.

```

### Selecting/Extracting only up or down regulating genes
```{r, eval=TRUE, echo=TRUE}
genes_up <- rownames(fit.1.rma)[results[,2] == 1]       #list of upregulating genes
genes_down <- rownames(fit.1.rma)[results[,2] == -1]    #list of down regulating genes
genes_diff <- rownames(fit.1.rma)[results[,2] != 0]     #list of genes differently expressed

#Copying up/down regulated genes
as.data.frame(genes_up) %>% write.csv("/media/lab-admin/VS_lab_disk/Lakshmi_working_data/microarray_data_varadha/output_430B/genes_upregulated.csv")
as.data.frame(genes_down) %>% write.csv("/media/lab-admin/VS_lab_disk/Lakshmi_working_data/microarray_data_varadha/output_430B/genes_downregulated.csv")
```

### The Venn Diagram
```{r, eval=TRUE, echo=TRUE}
vennDiagram(results)
vennDiagram(results,c("up", "down"),
            counts.col=c("red", "blue"),
            circle.col = c("red", "blue"))
```
### The HeatMap of top-ranked genes

```{r, eval=TRUE, echo=TRUE}

gplots::heatmap.2(dat_sel$coefficients,
                  key=TRUE,
                  density.info="none",
                  trace="none",
                  cexCol = 0.7,
                  col=hmcols,
                  scale="none")

```

