``` {r}
library(ggplot2)
library(dplyr)
library(magrittr)
```

```{r}
base_path <- "/Users/lakshmibalasubramanian/Documents/Lakshmi/SurfaceArea_analysis_new_Jun17"
#setwd("/Users/lakshmibalasubramanian/Documents/Lakshmi/SurfaceArea_analysis_new_Jun17")
dirnames <- list.dirs(base_path, recursive = FALSE)
#dat_inf <- list()
for (i in 1:length(dirnames)){
  file_timepoint <- list.dirs(dirnames[i], recursive = FALSE)
  print(file_timepoint)
  filenames <- list.files(dirnames[i], recursive = TRUE)
  file_name_temp <- list.files(dirnames[i])
  nam_col <- file_name_temp[i]
  #file_timepoint <- file_timepoint[-1]
  print(length(file_timepoint))
  #print(filenames)
  loca_inf <- list(list())
  for (j in 1:length(file_timepoint)){
    #--------------Infected cell--------------------
    filenames_inf <-
       c("statistics_inf_cell.csv",
          "statistics_inf_surfacearea_BC.csv")
    dat_inf <- list()

    for(i in 1:length(filenames_inf)){
      dat_inf[[i]] <- readr::read_csv(sprintf("%s/%s", file_timepoint[j], filenames_inf[[i]]))
    }
    
    names(dat_inf) <- filenames_inf
    dat_cell_inf <- dat_inf[grep("cell", names(dat_inf))]
    dat_saBC_inf <- dat_inf[grep("surfacearea_BC", names(dat_inf))]
    dat_saBC_inf[is.na(dat_saBC_inf)] <- 0
    
    loca_inf[[j]] <- 
      cbind(
        lapply(dat_cell_inf, function(x) x[[2]]) %>% as.matrix(),
        lapply(dat_saBC_inf, function(x) x[[3]] %>% sum()/2) %>% as.matrix(), 
        lapply(dat_saBC_inf, function(x) x[[5]] %>% sum()/2) %>% as.matrix()
        ) %>% as.data.frame()
    
    loca_inf[[j]] <- plyr::colwise(as.numeric)(loca_inf[[j]])
    loca_inf$Status <- "INF"
    loca_inf$File <- nam_col
    #colnames(loca_inf[[j]]) <- c("cell_Vol", "saBC_SA", "saBC_SV" , "Status","File Name")
    total_temp <- loca_inf[[j]]
    #total <- rbind(total_temp,loca_inf)
    
    
    #---------------PVM----------------------------

    file.rename(from = file.path(file_timepoint[j], "statistics_PVM.csv"), to = file.path(file_timepoint[j], "statistics_PVM_cell.csv"))

    filenames_pvm <-
      c("statistics_PVM_cell.csv",
          "statistics_PVM_surfacearea_BC.csv")
    
    dat_pvm <- list()
    
    for(i in 1:length(filenames_pvm)){
        dat_pvm[[i]] <- readr::read_csv(sprintf("%s/%s", file_timepoint[j], filenames_pvm[[i]]))
    }
    names(dat_pvm) <- filenames_pvm

    dat_cell_pvm <- dat_pvm[grep("cell", names(dat_pvm))]
    dat_saBC_pvm <- dat_pvm[grep("surfacearea_BC", names(dat_pvm))]

    if (dat_saBC_pvm %>% as.data.frame() %>% nrow() == 0) {
        dat_saBC_pvm[[1]][1,] <- 0 
        dat_saBC_pvm[[1]] <- plyr::colwise(as.numeric)(dat_saBC_pvm[[1]])
      }

    loca_pvm <- 
          cbind(
                lapply(dat_cell_pvm, function(x) x[[2]]) %>% as.matrix(),
                lapply(dat_saBC_pvm, function(x) x[[3]] %>% as.numeric() %>% sum()/2) %>% as.matrix(), 
                lapply(dat_saBC_pvm, function(x) x[[5]] %>% as.numeric() %>% sum()/2) %>% as.matrix()
              ) %>% as.data.frame()


    loca_pvm <- plyr::colwise(as.numeric)(loca_pvm)
    loca_pvm$Status <- "PVM"
    loca_pvm$File <- nam_col
    colnames(loca_pvm) <- c("cell_Vol", "saBC_SA", "saBC_SV", "Status","File Name")
    
  }
  loca_inf_final <- loca_inf[[j]] %>% bind_rows()
  View(loca_inf_final)
  total <- rbind(loca_pvm,loca_inf[[j]])

  write.csv(total, file = file.path(base_path,"results.csv"))
  colnames(total) <- c( "cell_Vol", "saBC_SA", "saBC_SV", "Status","File Name")
  #write.table(total, file = file.path(main_path, "master_results.csv"), append=TRUE, sep = ",", col.names = FALSE)
}
```

#--------------Infected cell--------------------
filenames_inf <-
  c("statistics_inf_cell.csv",
    "statistics_inf_surfacearea_BC.csv")

dat_inf <- list()

for(i in 1:length(filenames_inf)){
  dat_inf[[i]] <- readr::read_csv(sprintf("%s/%s", path, filenames_inf[[i]]))
}
names(dat_inf) <- filenames_inf

dat_cell_inf <- dat_inf[grep("cell", names(dat_inf))]
dat_saBC_inf <- dat_inf[grep("surfacearea_BC", names(dat_inf))]
dat_saBC_inf[is.na(dat_saBC_inf)] <- 0

loca_inf <- 
  
  cbind(
    lapply(dat_cell_inf, function(x) x[[2]]) %>% as.matrix(),
    lapply(dat_saBC_inf, function(x) x[[3]] %>% sum()/2) %>% as.matrix(), 
    lapply(dat_saBC_inf, function(x) x[[5]] %>% sum()/2) %>% as.matrix()
  ) %>% as.data.frame()
loca_inf <- plyr::colwise(as.numeric)(loca_inf)
loca_inf$Status <- "INF"
loca_inf$File <- nam_col
colnames(loca_inf) <- c("cell_Vol", "saBC_SA", "saBC_SV" , "Status","File Name")


#---------------PVM----------------------------

file.rename(from = file.path(path, "statistics_PVM.csv"), to = file.path(path, "statistics_PVM_cell.csv"))

filenames_pvm <-
  c("statistics_PVM_cell.csv",
    "statistics_PVM_surfacearea_BC.csv")

dat_pvm <- list()

for(i in 1:length(filenames_pvm)){
  dat_pvm[[i]] <- readr::read_csv(sprintf("%s/%s", path, filenames_pvm[[i]]))
}

names(dat_pvm) <- filenames_pvm

dat_cell_pvm <- dat_pvm[grep("cell", names(dat_pvm))]
dat_saBC_pvm <- dat_pvm[grep("surfacearea_BC", names(dat_pvm))]

if (dat_saBC_pvm %>% as.data.frame() %>% nrow() == 0) {
  dat_saBC_pvm[[1]][1,] <- 0 
  dat_saBC_pvm[[1]] <- plyr::colwise(as.numeric)(dat_saBC_pvm[[1]])
}


loca_pvm <- 
  cbind(
    lapply(dat_cell_pvm, function(x) x[[2]]) %>% as.matrix(),
    lapply(dat_saBC_pvm, function(x) x[[3]] %>% as.numeric() %>% sum()/2) %>% as.matrix(), 
    lapply(dat_saBC_pvm, function(x) x[[5]] %>% as.numeric() %>% sum()/2) %>% as.matrix()
  ) %>% as.data.frame()


loca_pvm <- plyr::colwise(as.numeric)(loca_pvm)
loca_pvm$Status <- "PVM"
loca_pvm$File <- nam_col
colnames(loca_pvm) <- c("cell_Vol", "saBC_SA", "saBC_SV", "Status","File Name")


#-----------------Uninfected hepatocytes (5 cells)--------------------
filenames_uninf <- 
  c("1statistics_uninf_cell.csv",
    "1statistics_uninf_surfacearea_BC.csv",
    "2statistics_uninf_cell.csv",
    "2statistics_uninf_surfacearea_BC.csv",
    "3statistics_uninf_cell.csv",
    "3statistics_uninf_surfacearea_BC.csv",
    "4statistics_uninf_cell.csv",
    "4statistics_uninf_surfacearea_BC.csv",
    "5statistics_uninf_cell.csv",
    "5statistics_uninf_surfacearea_BC.csv")
dat <- list()

for(i in 1:length(filenames_uninf)) {
  dat[[i]] <- readr::read_csv(sprintf("%s/%s", path, filenames_uninf[[i]]))
}
names(dat) <- filenames_uninf

dat_cell <- dat[grep("cell", names(dat))]
dat_saBC <- dat[grep("surfacearea_BC", names(dat))]
dat_saBC[is.na(dat_saBC)] <- 0

loca <- 
cbind(
  lapply(dat_cell, function(x) x[[2]]) %>% as.matrix(), 
  lapply(dat_saBC, function(x) x[[3]] %>% sum()/2) %>% as.matrix(), 
  lapply(dat_saBC, function(x) x[[5]] %>% sum()/2) %>% as.matrix()
) %>% 
  as.data.frame()

loca <- plyr::colwise(as.numeric)(loca)
plyr::colwise(mean)(loca)
loca$Status <- "UNINF"
loca$File <- nam_col
colnames(loca) <- c( "cell_Vol", "saBC_SA", "saBC_SV", "Status","File Name")
#dat_saBC$`1statistics_uninf_surfacearea_BC.csv`[[4]] %>% sum()


total <- rbind(loca_pvm,loca_inf,loca)
write.csv(total, file = file.path(path,"results.csv"))
colnames(total) <- c( "cell_Vol", "saBC_SA", "saBC_SV", "Status","File Name")
write.table(total, file = file.path(main_path, "master_results.csv"), append=TRUE, sep = ",", col.names = FALSE)
}

```

